H<sub>1</sub>: Derogations and emergency policies

### 2023-04-21 analysis/analysis_policies.qmd
Update model definition

$$
\begin{aligned}
\text{COVID policy}_{i, t} \sim&\ \operatorname{Bernoulli}(\pi_{i, t}) \\[0.75em]
\operatorname{logit}(\pi_{i, t}) =&\ \alpha_{\text{country} [i]} + \beta_1\ \text{Derogation in effect}_{i}\ + \\
&\ \beta_2\ \text{New cases}_{i}\ + \beta_3\ \text{Cumulative cases}_{i}\ + \\
&\ \beta_4\ \text{New deaths}_{i}\ + \beta_5\ \text{Cumulative deaths}_{i}\ + \\
&\ \beta_6\ \text{Week number}_{i} \\
\alpha_j \sim&\ \mathcal{N}(\bar{\alpha}, \sigma_\alpha) \text{, for } j \text{ in } 1 \dots J \\[0.75em]
\bar{\alpha} \sim&\ \operatorname{Student t}(\nu = 1, \mu = 0, \sigma = 3) \\
\beta_{1 \dots 6} \sim&\ \operatorname{Student t}(\nu = 1, \mu = 0, \sigma = 3) \\
\sigma_a \sim&\ \operatorname{Cauchy}(x = 0, \gamma = 1) \text{, lower bound} = 0
\end{aligned}
$$

>>>>

$$
\begin{aligned}
\text{COVID policy}_{i, t} \sim&\ \operatorname{Bernoulli}(\pi_{i, t}) \\[0.75em]
\operatorname{logit}(\pi_{i, t}) =&\ \alpha_{\text{region} [i]} + \beta_1\ \text{Derogation in effect}_{i}\ + \\
&\ \beta_2\ \text{New cases}_{i}\ + \beta_3\ \text{Cumulative cases}_{i}\ + \\
&\ \beta_4\ \text{New deaths}_{i}\ + \beta_5\ \text{Cumulative deaths}_{i}\ + \\
&\ \beta_6\ \text{Past ICCPR derogation}_{i}\ + \beta_7\ \text{Past ICCPR action}_{i}\ + \\
&\ \beta_8\ \text{Rule of law index}_{i}\ + \beta_9\ \text{Civil liberties index}_{i}\ + \\
&\ \beta_{10}\ \text{Core civil society index}_{i}\ + \beta_{11}\ \text{Week number}_{i} \\
\alpha_j \sim&\ \mathcal{N}(\bar{\alpha}, \sigma_\alpha) \text{, for } j \text{ in } 1 \dots J \\[0.75em]
\bar{\alpha} \sim&\ \operatorname{Student t}(\nu = 1, \mu = 0, \sigma = 3) \\
\beta_{1 \dots 11} \sim&\ \operatorname{Student t}(\nu = 1, \mu = 0, \sigma = 3) \\
\sigma_a \sim&\ \operatorname{Cauchy}(x = 0, \gamma = 1) \text{, lower bound} = 0
\end{aligned}
$$
